Analyzing difficulty of Wordle using aggregate Twitter responses to determine public reaction

### 2022-04-27 outputs/paper/paper.Rmd
adding further script cleaning and additions/modifications to introduction/data/model sections of paper

---
title: "Analyzing difficulty of Wordle using aggregate Twitter responses to determine public reaction"
subtitle: "My subtitle if needed"
author: 
  - Ivan Li
thanks: "Code and data are available at: https://github.com/Ivannoar/Twilight."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Using the Twitter API, data was gathered recording the public scores of Wordle players over one month. The frequency of each daily score was obtained and analyzed based on level of success, time, and geographical location. It was found that ___. These results may have significance in literary and linguistic analysis."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

library(tidyverse)
```

@@

This paper aims to analyze several metrics of Wordle's popularity on Twitter. As a result of millions of users sharing their scores each day, analysis can and has been done on variables including average score- a recent study found that Sweden was the country with the lowest average guesses with 3.72 average guesses out of a maximum of 6. Here, some key findings we wish to seek include attempting to model whether certain characteristics of a word correlate with its average difficulty, whether players have been improving in the game since its rise in popularity, and if the time of completion since the game resetting has any correlation with the average score. These metrics were not discussed deeply in prior papers and may be of interest to future puzzle makers, linguists, and game theorists.

Using the Twitter API, tweets pertaining to Wordle were gathered from various time periods in Wordle's popularity. The periods analyzed were the weeks following the game's rise in popularity, and the most recent week at time of writing (March 27 - April 2 2022). User scores were collected and aggregated along with time of posting, geographical location, and other data provided by Twitter. The results were turned into graphical data and analyzed according to our key missions.

@@

@@

>>>>

---
title: "Analyzing difficulty of Wordle using aggregate Twitter responses to determine public reaction"
subtitle: "My subtitle if needed"
author: 
  - Ivan Li
thanks: "Code and data are available at: https://github.com/Ivannoar/Twilight."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Using the Twitter API, data was gathered recording the public scores of Wordle players over one month. The frequency of each daily score was obtained and analyzed based on level of success, geographical location, and properties of the word. It was found that ___. These results may have significance in literary and linguistic analysis."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

library(tidyverse)
library(kableExtra)
library(countrycode)
library(chron)
```

@@

This paper aims to analyze several metrics of Wordle's popularity on Twitter. As a result of millions of users sharing their scores each day, analysis can and has been done on variables including average score- a recent study found that Sweden was the country with the lowest average guesses with 3.72 average guesses out of a maximum of 6. Here, some key findings we wish to seek include attempting to model whether certain characteristics of a word correlate with its average difficulty, and the average score of Twitter users in relation to their geographical location, such as their country of residence. These metrics were not discussed deeply in prior papers and may be of interest to future puzzle makers, linguists, and game theorists.

Using the Twitter API, tweets pertaining to Wordle were gathered and aggregated into multiple datasets used for analysis. These tweets were gathered during intervals from April 4-10 2022, and April 17-23 2022). User scores were collected by searching for common templates that are used by the website domain to share scores in their tweets. Along with the score the used reached, the time of posting, geographical location, and other data provided by Twitter were also obtained. The results were turned into graphical data and analyzed according to our key missions.

@@

```{r}

set.seed(1234)

simulated_data <-
  tibble(
    'Date' = sample(seq(as.Date('2022/04/05'), as.Date('2022/04/23'), by="day"), 10, replace = TRUE),

    'Time' = sample(format(seq(as.POSIXct('00:00:00', format = "%T"), 
                    as.POSIXct('23:59:59', format = "%T"), by = "sec"), "%T"), 10, replace = TRUE),
    'Location' = sample(countrycode::codelist$country.name.en, 10),     
    'Score' = sample(x = c('1/6', '2/6', '3/6', '4/6', '5/6', '6/6', 'DNF'), 10, replace = TRUE),
    'Hardmode' = sample(c(TRUE, FALSE), 10, replace = TRUE)
  )
simulated_data
```

```{r}
masterdata_clean |>
  slice(1:5) |>
  kable(
    caption = "First five rows of a dataset showing Wordle-related tweets",
    col.names = c("Date", "Time", "Country", "Country Code", "Wordle Score", "Hardmode"),
    digits = 1,
    booktabs = TRUE, 
    linesep = ""
  ) |> kable_styling(latex_options = c("striped", "scale_down"))

```

```{r}
masterdata_clean |>
  filter(hardmode == TRUE) |>
  ggplot(mapping = aes(x = score)) + geom_bar()

masterdata_clean |>
  filter(hardmode == FALSE) |>
  ggplot(mapping = aes(x = score)) + geom_bar()

masterdata_clean |>
  ggplot(mapping = aes(x = score, fill = hardmode)) + geom_bar()

```

```{r}

data_firstweek |>
  ggplot(mapping = aes(x = score, fill = as.character(date_tweeted))) + geom_bar(position = "dodge")

```

```{r}

average_score_df <- masterdata_clean |>
  group_by(date_tweeted) |>
  transmute(average_score = mean(as.numeric(score))) |>
  unique() |>
  arrange(date_tweeted, desc(date_tweeted))

average_score_df <- average_score_df[-c(15, 16), ]

average_score_df$daily_word <- c("Shawl", "Natal", "Comma", "Foray", "Scare", "Stair", "Black",
                                 "Ample", "Flair", "Foyer", "Cargo", "Oxide", "Plant", "Olive")

average_score_df$rank <- c("11938", "26852", "11931", "10467", "3837", "2880", "253",
                                 "6374", "11502", "9811", "4953", "10008", "623", "6242")

average_score_df |> 
  kable(
    caption = "Average score of Twitter Wordle players",
    col.names = c("Date", "Average Score", "Daily Word", "Word Frequency Rank"),
    digits = 1,
    booktabs = TRUE, 
    linesep = ""
  ) |> 
  kable_styling(latex_options = c("striped", "scale_down"))

```

@@

In this paper, we seek to use a regression model to determine if there were relationships between the average score that Twitter users scored daily and properties of the given word for the day. We aim to use both continuous and dummy variables in our regression model, so logistic regression models will be used to fulfill this purpose. These logistic regression models were able to conclude that ______.
The models are shown as follows, with one continuous variable and one binary variable:

model here
